Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-06 paper/paper.tex
introduction improved

\section{Introduction}
Looking at the field of artificial neuronal networks (NN), one finds a great
variety of different models describing both the dynamic of networks as well
as their plasticities, i.e.\ their learning behavior. 
But, given some dynamics and plasticity rules, which features of a network
determine, if it is a good candidate for doing a specific task?
%But what exactly makes artificial neuronal networks learn successfully? And
%why are certain types of networks and certain learning rules effective for
%some problems, but fail at solving others? 
%Confronting and eventually
%answering these questions is critical when trying to gain a deep
%understanding of neural networks and artificial intelligence.

Using this question as a guideline, we decided to examine network
characteristics that make the FORCE algorithm \citep{FORCE} especially
suitable for learning periodic patterns. More precisely, we wanted to
identify which high level properties of a NN are important for its learning
success under FORCE, and how to choose their values for an optimal result.

@@

To address these issues we introduce \emph{network genotypes}, which
contain parametric information about the networks (\emph{phenotypes}) to be
created: Different phenotypes of the same genotype may have strong
differences in detail, but they share structural qualities of interest.
Improving these genotypes for a specific range of tasks via genetic
optimization is the main concern of this article.
%The fitness of these genotypes for a specific range of tasks was optimized 
%using genetic algorithms.
%whose fitness
%for a preassigned range of tasks we analyze and improve with genetic
%optimization.
% TODO we say the same thing later on again. maybe, the comment about the genetic algorithm
% should be moved out of the parenthesis
%Since calculating the fitness of a genotype requires the evaluation of many
%different phenotypes and because of the resulting stochastic nature of the
%problems we faced, we decided to use genetic algorithms for the
%optimization process.

>>>>

\section{Introduction}
Looking at the field of artificial neuronal networks (NN), one finds a great
variety of different models describing both the dynamic of networks as well
as their plasticities, i.e.\ their learning behavior. 
But, given some dynamics and plasticity rules, which features of a network
determine whether it is a good candidate for doing a specific task?
%But what exactly makes artificial neuronal networks learn successfully? And
%why are certain types of networks and certain learning rules effective for
%some problems, but fail at solving others? 
%Confronting and eventually
%answering these questions is critical when trying to gain a deep
%understanding of neural networks and artificial intelligence.

%Using this question as a guideline, we decided to examine network
%characteristics that make the FORCE algorithm \citep{FORCE} especially
%suitable for learning periodic patterns. More precisely, we wanted to
%identify which high level properties of a NN are important for its learning
%success under FORCE, and how to choose their values for an optimal result.

Using this question as a guideline, we decided to analyze which high level
properties of a NN are important for its learning success under a variant
of the FORCE algorithm \citep[Architecture A]{FORCE}, and how to choose
their values for an optimal result.

@@

To address these issues in the context of genetic algorithms, we introduce
\emph{network genotypes}, which contain parametric information about the
networks (\emph{phenotypes}) to be created: Different phenotypes of the
same genotype may have strong differences in detail, but they share
structural qualities of interest.  Improving these genotypes for a specific
range of tasks via genetic optimization is the main concern of this
article.
%The fitness of these genotypes for a specific range of tasks was optimized 
%using genetic algorithms.
%whose fitness
%for a preassigned range of tasks we analyze and improve with genetic
%optimization.
% TODO we say the same thing later on again. maybe, the comment about the genetic algorithm
% should be moved out of the parenthesis
%Since calculating the fitness of a genotype requires the evaluation of many
%different phenotypes and because of the resulting stochastic nature of the
%problems we faced, we decided to use genetic algorithms for the
%optimization process.
